### 2023-03-15 main.tex
DescriptionOfHoles

{\color{blue}We consider the stirring process with an arbitrary number of particles $N$. It is important to note that any one of them can be considered the empty (or hole) particle. Thus, in this first general setting we do not distinguish between real and empty particles. However, this distinction will be useful in the section about duality, where we will see that this empty will play a special role. The stochastic dynamics is Markovian and consist in an exchange of particles of any type between two connected site of a graph.}

@@

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\Big(E_{k\ell}^{x} E_{\ell k}^{y}-E_{\ell\ell}^{x} E_{kk}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

>>>>

The process studied in this paper is the multi-species stirring process on the geometry of a graph. We consider the general situation where at any time and at any site a mixture of $\nu\in \mathbb{N}$, chosen among $N$ possible species (sometimes called types or colors), is present. Among these $N$ types of particles we will distinguish $N-1$ actual types, labelled with $k\in \{2,\ldots,N\}$ and a 'hole', labelled with $1$. This is an arbitrary choice, indeed one could call any of the $N$ colors the hole. In the description of the dynamic this choice is not important, since one could think about the dynamic as a pure exchange of types between sites, under the constraint that the maximal occupancy at each site is $\nu$. However, studying the duality for the boundary driven case, it will be important to chose an hole type, in order to interpret the dual dynamic as absorbing, i.e. to have, eventually, an empty dual process on the graph. Furthermore, one could think about the hole type as the only type whose occupation dependes on the occupations of all the true $N-1$ colors. In the two species case, this multi-species stirring process, is the SEP($\nu$) (see \cite{giardina2009duality}, \cite{carinci2013duality}). Indeed one of the two type is the hole (say again $1$) and its dynamics depends on the one of the true type (say 2), under the constaraint that at most $\nu$ type $2$ particles are present at a site at each time. Therefore, the dynamics can be describe only by species $2$. It is interesting to observe that, in case we stop distinguishing the colors of the true particles $\{2,\ldots,N\}$, we retrieve the SEP($\nu$), thus this multi-species stirring process seems its natural generalization.

@@

%We now define the equivalent of \eqref{stateSpace} in the vector notation
% \begin{equation}
%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
%	\end{equation}
%where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
\end{equation}
where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$ the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$. The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}
We introduce the Hamiltonian operator

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\Big(E_{k\ell}^{x} E_{\ell k}^{y}-E_{\ell\ell}^{x} E_{kk}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}
